Holographic duality beyond AdS/CFT

### 2021-11-28 alpha/BeyondAdSCFT/beyondAdS.tex
Add comments on the symmetric orbifold & S-dual

	We have thus discovered two equivalent descriptions of the D1-D5-$P$ system, summarized as follows:
	\begin{equation*}
	\begin{array}{ccc}
		\pqty{
			\ \begin{gathered}
				\text{Far-region dynamics} \\
				+ \\
				\text{Strings on $\ads{3}\times S^3\times \mcal{M}_4$}
			\end{gathered}\ %
		}
		&=&
		\pqty{
			\ \begin{gathered}
				\text{Far-region dynamics} \\
				+ \\
				\text{S\cft{2} with target $\mcal{M}_4$}
				\vphantom{S^3}
			\end{gathered}\ %
		}
	\\[6ex]
		\textit{Closed string picture}
		& &
		\textit{Open string picture}
	\end{array}
	\end{equation*}
	The far-region dynamics decouple on both sides, and we have the following proposal of an \ads{3}/\cft{2} duality:
	\begin{equation}
	\begin{aligned}
		&\text{Type IIB string theory on $\ads{3}\times S^3\times \mcal{M}_4$} \\
		{} = {}
		&\text{Deformations of some $\mcal{N} = (4,4)$ S\cft{2} with target $\mcal{M}_4$}
	\end{aligned}
	\end{equation}
	\sidenote{Deformations? Symmetric orbifolds?}

@@

>>>>

	We have thus discovered two equivalent descriptions of the D1-D5-$P$ system, summarized as follows:
	\begin{equation*}
	\begin{array}{ccc}
		\pqty{
			\ \begin{gathered}
				\text{Far-region dynamics} \\
				+ \\
				\text{Strings on $\ads{3}\times S^3\times \mcal{M}_4$}
			\end{gathered}\ %
		}
		&=&
		\pqty{
			\ \begin{gathered}
				\text{Far-region dynamics} \\
				+ \\
				\text{S\cft{2} with target $\mcal{M}_4$}
				\vphantom{S^3}
			\end{gathered}\ %
		}
	\\[6ex]
		\textit{Closed string picture}
		& &
		\textit{Open string picture}
	\end{array}
	\end{equation*}
	The far-region dynamics decouple on both sides, and we have the following proposal of an \ads{3}/\cft{2} duality \needcites:
	\begin{equation}
	\begin{aligned}
		&\text{Type IIB string theory on $\ads{3}\times S^3\times \mcal{M}_4$} \\
		{} = {}
		&\text{Marginal deformations of some $\mcal{N} = (4,4)$ S\cft{2} with target $\mcal{M}_4$}
	\end{aligned}
	\end{equation}
	Note that both sides of the duality includes a non-trivial moduli \needcites. \wx{In particular, the S\cft{2} on the right-hand side is proposed to be a \textit{symmetric product orbifold theory} \needcites, together with its exactly marginal deformations along the conformal manifold. }{elaborate?}

@@

	The D1-D5-$P$ system is tough to deal with on the worldsheet, within the framework of the RNS (or NSR) formalism, due to its non-trivial coupling to the R-R field $C_2$. This difficulty can be avoided by considering its S-dual, the NS1-NS5-$P$ system.

	On the other hand, we can make use of the $\mrm{SL}(2,\mbb{Z})$ duality from type IIB string theory.
